plots with prolactin

### 2019-12-30 analysis/16_PRL.Rmd
new PRL and BRCA figures

```{r hormone}
p1 <- hormones %>% 
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() %>% 
  ggplot(aes(x = treatment, y = plasma_conc, fill = treatment)) +
    geom_boxplot() +
  ylim(c(-10,120)) + 
    theme_B3() +
  #theme(axis.text.x = element_blank()) + 
  theme(legend.position = "none") + 
  labs(x = "parental care stages", y = "prolactin (ng/mL)") +
  annotation_custom(control, ymin = -20, ymax = 0, xmin = -7.5) +
  annotation_custom(bldg, ymin = -20, ymax = 0, xmin = -5.5) +
  annotation_custom(lay, ymin = -20, ymax = 0, xmin = -3.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -1.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 0.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 2.5) +
  annotation_custom(hatch, ymin = -20, ymax = 0, xmin = 4.5) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 6.5) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 8.5) 
p1

p2 <-  ggplot(meanprolactin, aes(treatment, m)) +
  geom_errorbar(aes(ymin=m-se, ymax=m+se, color = treatment), width=.1) +
   geom_image(aes(image=iconpath), size=.1)  +
  labs(x = "parental care stages", y = "prolactin (ng/mL)") +
  theme_B3() +
  theme(legend.position = "none")

p2

p3 <- ggplot(meanprolactin, aes(treatment, m)) +
   geom_image(aes(image=music), size=.12)  +
  labs(x = "increasing time >>", y = "prolactin (ng/mL)")  +
  mytheme() +
  ylim(c(-15,80)) +
  annotation_custom(control, ymin = -20, ymax = 0, xmin = -7.5) +
  annotation_custom(bldg, ymin = -20, ymax = 0, xmin = -5.5) +
  annotation_custom(lay, ymin = -20, ymax = 0, xmin = -3.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -1.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 0.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 2.5) +
  annotation_custom(hatch, ymin = -20, ymax = 0, xmin = 4.5) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 6.5) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 8.5) +
  geom_hline(yintercept=0) +
  geom_hline(yintercept=20) +
  geom_hline(yintercept=40) +
  geom_hline(yintercept=60) +
  geom_hline(yintercept=80) 
p3

p4 <- hormones %>% 
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() %>% 
  ggplot(aes(x = treatment, y = plasma_conc)) +
    geom_boxplot(aes(fill = treatment, alpha = sex, color = sex)) +
    theme_B3() +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = "prolactin (ng/mL)", x = NULL) +
    guides(fill = FALSE, alpha = FALSE,
         color = guide_legend(order=1)) +
    scale_alpha_manual(values = c(0.75,1)) +
    theme(legend.position = c(0.85,0.15), legend.direction = "horizontal") + 
  labs(x = "increasing time >>", y = "prolactin (ng/mL)") +
  annotation_custom(control, ymin = -20, ymax = 0, xmin = -7.8) +
  annotation_custom(bldg, ymin = -20, ymax = 0, xmin = -5.8) +
  annotation_custom(lay, ymin = -20, ymax = 0, xmin = -3.8) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -1.8) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 0.6) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 2.4) +
  annotation_custom(hatch, ymin = -20, ymax = 0, xmin = 4.4) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 6.4) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 8.4) + 
  ylim(c(-10,120)) 
p4

plot_grid(p1,p4,p2,p3)

@@

```{r PRL.pit}
vsd.pit <- readvsd("../results/04_vsd_pit.csv")
colData.pit <- readcolData("../results/04_colData_pit.csv")

geneinfo <- read_csv("../metadata/00_geneinfo.csv") %>%  dplyr::select(Name, geneid, entrezid) %>% arrange(Name)
candidategenes <- c("PRL")
candidates.pit <- selectcandidatevsds(candidategenes, vsd.pit, colData.pit)

meanPRL <- candidates.pit %>% 
    droplevels() %>% 
  dplyr::group_by(treatment) %>%
  dplyr::summarise(m = mean(PRL), 
                   se = sd(PRL)/sqrt(length(PRL))) %>%
  dplyr::mutate(m = round(m,1)) 
meanPRL <- left_join(meanPRL, birds)
meanPRL$treatment <- factor(meanPRL$treatment, levels = alllevels)
meanPRL

p5 <- candidates.pit %>% 
  ggplot(aes(x = treatment, y = PRL, fill = treatment)) +
    geom_boxplot() +
    theme_B3() +
  theme(legend.position = "none") + 
  labs(x = "increasing time >>", y = "prolactin (ng/mL)") +
  annotation_custom(control, ymin = 12, ymax = 14, xmin = -7.8) +
  annotation_custom(bldg, ymin = 12, ymax = 14, xmin = -5.8) +
  annotation_custom(lay, ymin = 12, ymax = 14, xmin = -3.8) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = -1.8) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = 0.6) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = 2.4) +
  annotation_custom(hatch, ymin = 12, ymax = 14, xmin = 4.4) +
  annotation_custom(nestling, ymin = 12, ymax = 14, xmin = 6.4) +
  annotation_custom(nestling, ymin = 12, ymax = 14, xmin = 8.4)  +
  ylim(c(13,24)) 
p5

p6 <- ggplot(candidates.pit, aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, alpha = sex, color = sex)) + 
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
  theme(legend.position = c(0.85,0.2), legend.direction = "horizontal") + 
  scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
    labs(y = "PRL expression in the pituitary", x = "parental care stage") +
  annotation_custom(control, ymin = 12, ymax = 14, xmin = -7.8) +
  annotation_custom(bldg, ymin = 12, ymax = 14, xmin = -5.8) +
  annotation_custom(lay, ymin = 12, ymax = 14, xmin = -3.8) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = -1.8) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = 0.6) +
  annotation_custom(inc, ymin = 12, ymax = 14, xmin = 2.4) +
  annotation_custom(hatch, ymin = 12, ymax = 14, xmin = 4.4) +
  annotation_custom(nestling, ymin = 12, ymax = 14, xmin = 6.4) +
  annotation_custom(nestling, ymin = 12, ymax = 14, xmin = 8.4)  + 
  ylim(c(13,24)) +
  guides(fill = FALSE, alpha = FALSE, color = guide_legend(order=1)) 
p6

p7 <- ggplot(meanPRL, aes(treatment, m)) +
  geom_errorbar(aes(ymin=m-se, ymax=m+se, color = treatment), width=.1) +
   geom_image(aes(image=iconpath), size=.12)  +
  labs(x = "increasing time >>", y = "Pituitary PRL expression") +
  theme_B3()  +
  theme(legend.position = "none")
p7

p8 <- ggplot(meanPRL, aes(treatment, m)) +
   geom_image(aes(image=music), size=.12)  +
  labs(x = "parental care stages", y = "Pituitary PRL expression") +
  mytheme() +
  ylim(c(15,22)) +
  annotation_custom(control, ymin = 15, ymax = 16.5, xmin = -7.5) +
  annotation_custom(bldg, ymin = 15, ymax = 16.5, xmin = -5.5) +
  annotation_custom(lay, ymin = 15, ymax = 16.5, xmin = -3.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = -1.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = 0.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = 2.5) +
  annotation_custom(hatch, ymin = 15, ymax = 16.5, xmin = 4.5) +
  annotation_custom(nestling, ymin = 15, ymax = 16.5, xmin = 6.5) +
  annotation_custom(nestling, ymin = 15, ymax = 16.5, xmin = 8.5)   +
  geom_hline(yintercept=17) +
  geom_hline(yintercept=18) +
  geom_hline(yintercept=19) +
  geom_hline(yintercept=20) +
  geom_hline(yintercept=21)

plot_grid(p5,p6,p7,p8)
```

@@

```{r manipdata}
vsd.pit <- readvsd("../results/06_pitallvsd.csv")
vsd.pit$entrezid <- row.names(vsd.pit)

colData.pit <- read_csv("../metadata/00_samples.csv") %>% 
  filter(tissue == "pituitary") %>% 
  mutate(sample = V1)

geneinfo <- read_csv("../metadata/00_geneinfo.csv") %>%  
  dplyr::select(Name, geneid, entrezid) %>% arrange(Name)

candidategenes <- c("PRL")
candidates.pit <- selectcandidatevsds(candidategenes, vsd.pit, colData.pit)
candidates.pit$treatment <- factor(candidates.pit$treatment, levels = alllevels)

meanPRL <- candidates.pit %>% 
    droplevels() %>% 
  dplyr::group_by(treatment) %>%
  dplyr::summarise(m = median(PRL), 
                   se = sd(PRL)/sqrt(length(PRL))) %>%
  dplyr::mutate(m = round(m,1)) 
meanPRL <- left_join(meanPRL, birds)
meanPRL$treatment <- factor(meanPRL$treatment, levels = alllevels)
meanPRL
```

```{r PRL.pit.maip}
p10 <- ggplot(meanPRL, aes(treatment, m)) +
   geom_errorbar(aes(ymin=m-se, ymax=m+se, color = treatment), width=.1) +
   geom_image(aes(image = iconpath), size = 0.06)  +
   geom_image(aes(image = music , y = m + 0.5), size = 0.04) +
   labs(x = "parental care stages", y = "Pituitary PRL") +
   mytheme() +
   ylim(c(16,22)) +
   theme(axis.text.x = element_text(angle = 45)) +
  theme(legend.position = "none") +
  scale_color_manual(values = colorscharmaip2) +
  geom_hline(yintercept=16.8) +
  geom_hline(yintercept=17.8) +
  geom_hline(yintercept=18.8) +
  geom_hline(yintercept=19.8) +
  geom_hline(yintercept=20.8)  
p10

p11 <- ggplot(candidates.pit, aes(x = treatment, y = PRL)) + 
       geom_smooth(aes(colour = sex)) +
    geom_boxplot(aes(fill = treatment)) +
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
   theme(legend.position = "none", legend.direction = "horizontal") + 
   scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
    labs(y = "Pituitary PRL", x = NULL) +
  scale_fill_manual(values = colorscharmaip2) +
  ylim(c(13,22.5)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotation_custom(control, ymin = 13, ymax = 14, xmin = -14.8) +
  annotation_custom(bldg, ymin = 13, ymax = 14, xmin = -12.8) +
  annotation_custom(lay, ymin = 13, ymax = 14, xmin = -10.8) +
  annotation_custom(inc, ymin = 13, ymax = 14, xmin = -8.8) +
  annotation_custom(removeegg, ymin = 13, ymax = 14, xmin = -6.8) +
  annotation_custom(inc, ymin = 13, ymax = 14, xmin = -4.8) +
  annotation_custom(maniphatch, ymin = 13, ymax = 14, xmin = -2.8) +
  annotation_custom(removeegg, ymin = 13, ymax = 14, xmin = -0.8) +
  annotation_custom(inc, ymin = 13, ymax = 14, xmin = 1.4) +
  annotation_custom(removeegg, ymin = 13, ymax = 14, xmin = 3.4)  +
  annotation_custom(manipinc, ymin = 13, ymax = 14, xmin = 5.4) +
  annotation_custom(hatch, ymin = 13, ymax = 14, xmin = 7.4) +
  annotation_custom(removechick, ymin = 13, ymax = 14, xmin = 9.4) +
  annotation_custom(maniphatch, ymin = 13, ymax = 14, xmin = 11.4) +
  annotation_custom(nestling, ymin = 13, ymax = 14, xmin = 13.4) +
  annotation_custom(nestling, ymin = 13, ymax = 14, xmin = 15.4) 
p11

p12 <- candidates.pit %>%
  filter(treatment %in% c("inc.d9", "m.inc.d8", "hatch")) %>%
    ggplot(aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, color = sex)) + 
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
   theme(legend.position = "none", legend.direction = "horizontal") + 
   scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
    labs(y = "Pituitary PRL", x = NULL) +
  ylim(c(13,22.5)) +
  scale_fill_manual(values = colorscharmaip2)   +
  annotation_custom(control, ymin = 13, ymax = 14, xmin = -1.6) +
  annotation_custom(maniphatch, ymin = 13, ymax = 14, xmin = 0.4) +
  annotation_custom(hatch, ymin = 13, ymax = 14, xmin = 2.4)
p12

p13 <- candidates.pit %>%
  filter(treatment %in% c("inc.d17", "prolong", "hatch")) %>%
    ggplot(aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, color = sex)) + 
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
   theme(legend.position = "none", legend.direction = "horizontal") + 
   scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
    labs(y = "Pituitary PRL", x = NULL) +
  ylim(c(13,22.5)) +
  scale_fill_manual(values = colorscharmaip2)   +
  annotation_custom(control, ymin = 13, ymax = 14, xmin = -1.6) +
  annotation_custom(manipinc, ymin = 13, ymax = 14, xmin = 0.4) +
  annotation_custom(hatch, ymin = 13, ymax = 14, xmin = 2.4)
p13

p14 <- candidates.pit %>%
  filter(treatment %in% c("hatch", "extend", "n5")) %>%
    ggplot(aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, color = sex)) + 
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
   theme(legend.position = "none", legend.direction = "horizontal") + 
   scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
    labs(y = "Pituitary PRL", x = NULL) +
  ylim(c(13,22.5)) +
  scale_fill_manual(values = colorscharmaip2)   +
  annotation_custom(control, ymin = 13, ymax = 14, xmin = -1.6) +
  annotation_custom(maniphatch, ymin = 13, ymax = 14, xmin = 0.4) +
  annotation_custom(hatch, ymin = 13, ymax = 14, xmin = 2.4)
p14

plot_grid(p12,p13 + theme(axis.text.y = element_blank(), axis.title.y = element_blank()),
          p14 + theme(axis.text.y = element_blank(), axis.title.y = element_blank()), 
          nrow = 1, rel_widths = c(1.2,1,1))

@@

```{r geneshormones}
candidates.pit$bird_id <- candidates.pit$bird

geneshormones <- left_join(candidates.pit, hormones) %>%
  select(-X1, -V1, -okay, - icons, -music, -iconpath) %>%
  drop_na()
head(geneshormones)

@@

>>>>

```{r hormone}
p1 <- hormones %>% 
    filter(study == "characterization", hormone %in% c("prolactin"))  %>% 
    droplevels() %>% 
  ggplot(aes(x = treatment, y = plasma_conc)) +
    geom_boxplot(aes(fill = treatment, alpha = sex, color = sex)) +
    theme_B3() +
    scale_fill_manual(values = colorscharmaip) +
    scale_color_manual(values = sexcolors) +
    labs(y = "prolactin (ng/mL)", x = NULL) +
    guides(fill = FALSE, alpha = FALSE,
         color = guide_legend(order=1)) +
    scale_alpha_manual(values = c(0.75,1)) +
    theme(legend.position = c(0.85,0.15), legend.direction = "horizontal") + 
  labs(x = "increasing time >>", y = "prolactin (ng/mL)") +
  annotation_custom(control, ymin = -20, ymax = 0, xmin = -7.8) +
  annotation_custom(bldg, ymin = -20, ymax = 0, xmin = -5.8) +
  annotation_custom(lay, ymin = -20, ymax = 0, xmin = -3.8) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -1.8) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 0.6) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 2.4) +
  annotation_custom(hatch, ymin = -20, ymax = 0, xmin = 4.4) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 6.4) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 8.4) + 
  ylim(c(-10,120)) 
p1
```

```{r candidatevsds}
colData.pit <-  read.csv("../metadata/00_samples.csv", header = T, row.names = 1)
colData.pit <- colData.pit %>% filter(tissue == "pituitary")

vsd.pit <- read.csv("../results/06_pitallvsd.csv", header = T, row.names = 1)

savecols <- as.character(colData.pit$V1) 
savecols <- as.vector(savecols) 
vsd.pit <- vsd.pit %>% dplyr::select(one_of(savecols)) 
vsd.pit$genes <- row.names(vsd.pit)

candidategenes <- c("PRL", "BRCA1")
candidates.pit <- vsd.pit %>% dplyr::filter(genes %in% candidategenes)
candidates.pit <- as.data.frame(candidates.pit)
row.names(candidates.pit) <- candidates.pit$genes
candidates.pit$genes <- NULL
candidates.pit <- as.data.frame(t(candidates.pit))
candidates.pit$V1 <- row.names(candidates.pit) 
candidates.pit <- left_join(colData.pit, candidates.pit)
candidates.pit$treatment <- factor(candidates.pit$treatment, levels = alllevels)
tail(candidates.pit)
```

```{r PRL.pit}
meanPRL <- candidates.pit %>% 
    droplevels() %>% 
  dplyr::group_by(treatment, sex) %>%
  dplyr::summarise(m = mean(PRL), 
                   se = sd(PRL)/sqrt(length(PRL))) %>%
  dplyr::mutate(m = round(m,1))  %>%
  dplyr::filter(treatment %in% charlevels)
meanPRL <- left_join(meanPRL, birds)
meanPRL$treatment <- factor(meanPRL$treatment, levels = charlevels)
meanPRL

p2 <- candidates.pit %>%
  dplyr::filter(treatment %in% charlevels) %>%
  ggplot(aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, alpha = sex, color = sex)) + 
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
  theme(legend.position = c(0.85,0.2), legend.direction = "horizontal") + 
  scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
  labs(y = "PRL", x = "increasing time >>", subtitle = "Pituitary" ) +
  guides(fill = FALSE, alpha = FALSE, color = guide_legend(order=1)) +
  theme(axis.title.y  = element_text(face = "italic"))  +
  annotation_custom(control, ymin = 13.5, ymax = 15, xmin = -7.5) +
  annotation_custom(bldg, ymin = 13.5, ymax = 15, xmin = -5.5) +
  annotation_custom(lay, ymin = 13.5, ymax = 15, xmin = -3.5) +
  annotation_custom(inc, ymin = 13.5, ymax = 15, xmin = -1.5) +
  annotation_custom(inc, ymin = 13.5, ymax = 15, xmin = 0.5) +
  annotation_custom(inc, ymin = 13.5, ymax = 15, xmin = 2.5) +
  annotation_custom(hatch, ymin = 13.5, ymax = 15, xmin = 4.5) +
  annotation_custom(nestling, ymin = 13.5, ymax = 15, xmin = 6.5) +
  annotation_custom(nestling, ymin = 13.5, ymax = 15, xmin = 8.5)   
p2

@@

```{r PRLBRCA1}
meanBRCA <- candidates.pit %>% 
    droplevels() %>% 
  dplyr::group_by(treatment, sex) %>%
  dplyr::summarise(m = mean(BRCA1), 
                   se = sd(BRCA1)/sqrt(length(BRCA1))) %>%
  dplyr::mutate(m = round(m,1)) %>%
  dplyr::filter(treatment %in% charlevels)
meanBRCA <- left_join(meanBRCA, birds)
meanBRCA$treatment <- factor(meanBRCA$treatment, levels = alllevels)
meanBRCA

p3 <- candidates.pit %>% 
  dplyr::filter(treatment %in% charlevels) %>%
  ggplot(aes(x = treatment, y = BRCA1, fill = treatment, color = sex, alpha = sex)) +
    geom_boxplot() +
    theme_B3() +
      scale_alpha_manual(values = c(0.75,1)) +
  scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
  theme(legend.position = "none") + 
  labs(x = "increasing time >>", y = "BRCA1", subtitle = "Pituitary") +
  annotation_custom(control, ymin = 6.65, ymax = 7, xmin = -7.8) +
  annotation_custom(bldg, ymin = 6.65, ymax = 7, xmin = -5.8) +
  annotation_custom(lay, ymin = 6.65, ymax = 7, xmin = -3.8) +
  annotation_custom(inc, ymin = 6.65, ymax = 7, xmin = -1.8) +
  annotation_custom(inc, ymin = 6.65, ymax = 7, xmin = 0.6) +
  annotation_custom(inc, ymin = 6.65, ymax = 7, xmin = 2.4) +
  annotation_custom(hatch, ymin = 6.65, ymax = 7, xmin = 4.4) +
  annotation_custom(nestling, ymin = 6.65, ymax = 7, xmin = 6.4) +
  annotation_custom(nestling, ymin = 6.65, ymax = 7, xmin = 8.4) +
  ylim(6.8,8.5) +
  guides(fill = FALSE, alpha = FALSE, color = guide_legend(order=1)) +
  theme(legend.position = c(0.85,0.2), legend.direction = "horizontal") + 
  theme(axis.title.y  = element_text(face = "italic"))
p3

@@

```{r PRL.pit.maip}

p4 <- ggplot(candidates.pit, aes(x = treatment, y = PRL)) + 
    geom_boxplot(aes(fill = treatment, alpha = sex)) +
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
   theme(legend.position = "none", legend.direction = "horizontal") + 
   scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
  labs(x = "increasing time >>", y = "PRL", subtitle = "Pituitary") +
  scale_fill_manual(values = colorscharmaip2) +
  ylim(c(13,22.5)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotation_custom(control, ymin = 13, ymax = 14, xmin = -14.8) +
  annotation_custom(bldg, ymin = 13, ymax = 14, xmin = -12.8) +
  annotation_custom(lay, ymin = 13, ymax = 14, xmin = -10.8) +
  annotation_custom(inc, ymin = 13, ymax = 14, xmin = -8.8) +
  annotation_custom(removeegg, ymin = 13, ymax = 14, xmin = -6.8) +
  annotation_custom(inc, ymin = 13, ymax = 14, xmin = -4.8) +
  annotation_custom(maniphatch, ymin = 13, ymax = 14, xmin = -2.8) +
  annotation_custom(removeegg, ymin = 13, ymax = 14, xmin = -0.8) +
  annotation_custom(inc, ymin = 13, ymax = 14, xmin = 1.4) +
  annotation_custom(removeegg, ymin = 13, ymax = 14, xmin = 3.4)  +
  annotation_custom(manipinc, ymin = 13, ymax = 14, xmin = 5.4) +
  annotation_custom(hatch, ymin = 13, ymax = 14, xmin = 7.4) +
  annotation_custom(removechick, ymin = 13, ymax = 14, xmin = 9.4) +
  annotation_custom(maniphatch, ymin = 13, ymax = 14, xmin = 11.4) +
  annotation_custom(nestling, ymin = 13, ymax = 14, xmin = 13.4) +
  annotation_custom(nestling, ymin = 13, ymax = 14, xmin = 15.4) +
    theme(axis.title.y  = element_text(face = "italic"))
p4

@@

```{r BRCA.pit.maip}

p5 <- ggplot(candidates.pit, aes(x = treatment, y = BRCA1)) + 
    geom_boxplot(aes(fill = treatment, alpha = sex)) +
    scale_alpha_manual(values = c(0.75,1)) +
    theme_B3() +
   theme(legend.position = "none", legend.direction = "horizontal") + 
   scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
  labs(x = "increasing time >>", y = "BRCA1", subtitle = "Pituitary") +
  scale_fill_manual(values = colorscharmaip2) +
  ylim(6.8,8.5) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  annotation_custom(control, ymin = 13, ymax = 14, xmin = -14.8) +
  annotation_custom(bldg, ymin = 13, ymax = 14, xmin = -12.8) +
  annotation_custom(lay, ymin = 13, ymax = 14, xmin = -10.8) +
  annotation_custom(inc, ymin = 13, ymax = 14, xmin = -8.8) +
  annotation_custom(removeegg, ymin = 13, ymax = 14, xmin = -6.8) +
  annotation_custom(inc, ymin = 13, ymax = 14, xmin = -4.8) +
  annotation_custom(maniphatch, ymin = 13, ymax = 14, xmin = -2.8) +
  annotation_custom(removeegg, ymin = 13, ymax = 14, xmin = -0.8) +
  annotation_custom(inc, ymin = 13, ymax = 14, xmin = 1.4) +
  annotation_custom(removeegg, ymin = 13, ymax = 14, xmin = 3.4)  +
  annotation_custom(manipinc, ymin = 13, ymax = 14, xmin = 5.4) +
  annotation_custom(hatch, ymin = 13, ymax = 14, xmin = 7.4) +
  annotation_custom(removechick, ymin = 13, ymax = 14, xmin = 9.4) +
  annotation_custom(maniphatch, ymin = 13, ymax = 14, xmin = 11.4) +
  annotation_custom(nestling, ymin = 13, ymax = 14, xmin = 13.4) +
  annotation_custom(nestling, ymin = 13, ymax = 14, xmin = 15.4) +
    theme(axis.title.y  = element_text(face = "italic"))
p5

ggplot(candidates.pit, aes(x = PRL, y = BRCA1)) +
  geom_point(aes(alpha = sex,  color = 	treatment)) +
  geom_smooth(method = "loess", se=T, color = "darkgrey") +
  scale_color_manual(values = colorscharmaip2)  +
  scale_alpha_manual(values = c(0.5,1)) +
  labs(subtitle = "Pituitary") +
  theme(axis.title  = element_text(face = "italic"),
        legend.title =  element_blank())

```{r geneshormones}
candidates.pit$bird_id <- candidates.pit$bird
candidates.pit$X1 <- candidates.pit$V1
geneshormones <- left_join(candidates.pit, hormones) %>%
  select(-X1, -V1, -okay, - icons, -music, -iconpath) %>%
  drop_na()

(geneshormones$bird_id)
(hormones$bird_id)

@@

```{r music}

p8 <- ggplot(meanPRL, aes(treatment, m)) +
   geom_image(aes(image=music), size=.12)  +
  labs(x = "parental care stages", y = "PRL", subtitle = "Pituitary") +
  mytheme() +
  ylim(c(15,22)) +
  annotation_custom(control, ymin = 15, ymax = 16.5, xmin = -7.5) +
  annotation_custom(bldg, ymin = 15, ymax = 16.5, xmin = -5.5) +
  annotation_custom(lay, ymin = 15, ymax = 16.5, xmin = -3.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = -1.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = 0.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = 2.5) +
  annotation_custom(hatch, ymin = 15, ymax = 16.5, xmin = 4.5) +
  annotation_custom(nestling, ymin = 15, ymax = 16.5, xmin = 6.5) +
  annotation_custom(nestling, ymin = 15, ymax = 16.5, xmin = 8.5)   +
  geom_hline(yintercept=17) +
  geom_hline(yintercept=18) +
  geom_hline(yintercept=19) +
  geom_hline(yintercept=20) +
  geom_hline(yintercept=21)
